Verifying Concurrent Search Structure Templates for C Programs using VST

### 2023-04-14 concurrency/CONCUR 2023/paper.tex
fixed breakage

The proof starts with $\nodeboxrep \texttt{(pn->n)}$, which includes a pointer to the node's lock, the lock-invariant assertion of $\texttt{(pn->n)}$, and the resource $\texttt{R(pn->n)}$ obtained prior to calling the \lstinline{traverse} function. When \lstinline{findNext} successfully identifies the next node (for example, \lstinline{n'}) to visit, the lock invariant within $\nodeboxrep$ enables us to access the resource $\texttt{R(pn->n')}$ upon reaching line 14 in the C implementation of the lock-coupling template (Figure \ref{traverse_lock_b}). Following this, we release the lock of the current node (line 15 in Figure \ref{traverse_lock_b}), illustrating that we consistently maintain a single lock during node traversal.
\than{I feel somewhat perplexed while attempting to articulate the situation mentioned above. Can someone help me fix or explain it more?}

>>>>

The proof begins with $\nodeboxrep \texttt{(pn->n)}$, which comprises a pointer to the node's lock, the lock-invariant assertion of $\texttt{(pn->n)}$, and the resource $\texttt{R(pn->n)}$ acquired before invoking the \lstinline{traverse} function. When \lstinline{findNext} successfully detects the next node (e.g., \lstinline{n'}) to visit, the lock invariant within $\nodeboxrep$ allows us to access the resource $\texttt{R(pn->n')}$ at line 14 in the C implementation of the lock-coupling template (Figure \ref{traverse_lock_b}). Subsequently, we release the lock of the current node (line 15 in Figure \ref{traverse_lock_b}), demonstrating our consistent approach to maintaining a single lock during node traversal. The proof concludes by verifying that the \lstinline{traverse} function satisfies the post-condition of the specification mentioned earlier, owing to loop invariants \texttt{traverse\_inv\_1} and \texttt{traverse\_inv\_2}.

\than{I feel somewhat perplexed while attempting to articulate the situation mentioned above. Can someone help me fix or explain it more?}
